### 2020-10-08 thesis/msc-thesis.tex
formatting
add sections

% TITLE:
\pagenumbering{roman} 
\begin{titlepage}

\vspace*{1cm}
\begin{center}
\vspace*{3cm}
\textbf{ 
\Large Universität Heidelberg\\
\smallskip
\Large Institut für Informatik\\
\smallskip
\Large Arbeitsgruppe Datenbanksysteme\\
\smallskip
}

@@

\textbf{\large Bachelor-Arbeit}

\vspace{0.5\baselineskip}
{\huge
\textbf{Messaging Architecture for Integration of Customer Self-Services}
}
\end{center}

\vfill

{\large
\begin{tabular}[l]{ll}
Name: & Jonas Gann\\
Matriculation number: & 3367576\\
Supervisor: & Prof. Dr. Michael Gertz\\
Date of submission: & \today
\end{tabular}
}

@@

\begin{enumerate}
     \item Example(s) of CSS Problems Today
     \begin{enumerate}
          \item CSS incomplete in governmental administration
          \begin{enumerate}
               \item identity card renewal
               \item change of home address
               \item change of residency status 
          \end{enumerate}

@@

     \item Solution for CSS Problems
     \begin{enumerate}
          \item One CSS providing company, which integrates multiple / all EA
          \item One identity, profile, address, phone number, location, ...
          \item Easy management of identity used by multiple enterprises / organizations
     \end{enumerate}

     \item Why is integration necessary?
     \begin{enumerate}
          \item Each enterprise / organization has its own identities, profiles, etc. in multiple systems
          \item The CSS providing company needs to manage those systems / data of each enterprise / organization
          \item Enterprise Integration solves this Problem
     \end{enumerate}

@@

\begin{enumerate}
     \item What are challenges of integration?
     \begin{enumerate}
          \item Heterogeneous Enterprise Architecture Systems
          \begin{enumerate}
               \item Different Applications
               \item Different Application Vendors
               \item Different / No Application Interfaces
               \item Legacy Systems
          \end{enumerate}

@@

     \item How does the thesis solve the problems?
     \begin{enumerate}
          \item Messaging Integration
          \begin{enumerate}
               \item Loose Coupling
               \begin{enumerate}
                    \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
                    \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
                    \item Loose Coupling allows Reuse of "Modules" => faster development
               \end{enumerate}

@@

\chapter{Foundation and related work}
\label{chap:grundlagen}

\section{Customer Self-Service}
\begin{enumerate}
     \item What is CSS
     \begin{enumerate}
          \item Definition in the context of the thesis
     \end{enumerate}

     \item How to document CSS-Scenarios
     \item List of CSS-Scenarios
     \item Purpose of CSS-Scenarios in the thesis
     \begin{enumerate}
          \item Finding relevant EAPs
          \item Requirement analysis of business Connector
          \item Interface definition of business connector
     \end{enumerate}

\section{Architecture Patterns}
\begin{enumerate}
     \item What is an EAP
     \begin{enumerate}
          \item Definition
          \item Metadata
          \item Views
          \item Architecture bricks
          \item Data bricks
          \item Business processes
     \end{enumerate}

     \item Purpose of an EAP in this context
     \begin{enumerate}
          \item Basis for real-life enterprise architectures
          \item Provides architecture and data bricks the integration can build up on
     \end{enumerate}

     \item Short description of EAPs in the book
     \item Patterns relevant for CSS
     \begin{enumerate}
          \item Derived by comparing CSS-Scenarios with business processes
     \end{enumerate}

     \item Relevant Architecture bricks and data bricks for CSS-Scenarios
     \item How to document relevant bricks for usage of the integration Architecture
     \item Documentation of relevant bricks
     \item List of requirements regarding the integration Architecture
     \item \begin{enumerate}
          \item Adapters for systems
          \item Required Format of incoming data
     \end{enumerate}

\section{Business Connector}
\begin{enumerate}
     \item What is a business connector?
     \begin{enumerate}
          \item Provides functionality of "external" service provider
          \item Purpose is to simplify integration
          \item Can be assumed to provide sufficient interfaces
     \end{enumerate}

     \item Purpose of business connector in context of the thesis
     \begin{enumerate}
          \item Provides interface for CSS functionalities
          \item Should be integrated in architecture and data bricks
     \end{enumerate}

     \item How to document the business Connector in this context
     \begin{enumerate}
          \item List of provided functionalities along with their interfaces
          \begin{enumerate}
               \item Derived from CSS-Scenarios
               \item Derived from IDAS Connector
          \end{enumerate}

@@

\section{Integration Patterns}
\begin{enumerate}
     \item What are Integration Patterns?
     \begin{enumerate}
          \item Messaging Methodology
          \item Patterns describe often solved messaging problems
     \end{enumerate}

     \item What is their purpose in this context
     \begin{enumerate}
          \item Already explained in Motivation?
     \end{enumerate}

     \item Description of Patterns later used in the integration architecture
\end{enumerate}

@@

\chapter{My contribution}
\label{chap:main}

\section{Overview}
\label{sec:overview}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Experimental evaluation}
\label{chap:eval}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Summary and outlook}
\label{chap:concl}

>>>>

% TITLE:
\pagenumbering{roman}
\begin{titlepage}
     \vspace*{1cm}
     \begin{center}
          \vspace*{3cm}
          \textbf
          {
               \Large University of Heidelberg\\
               \smallskip
               \Large Institute for Computer Science\\
               \smallskip
               \Large Working group database systems\\
               \smallskip
          }

@@

          \textbf{\large Bachelor thesis}

          \vspace{0.5\baselineskip}
          {
               \huge
               \textbf{Messaging Architecture for Integration of Customer Self-Services}
          }

     \end{center}

     \vfill
     {
          \large
          \begin{tabular}[l]{ll}
               Name:                 & Jonas Gann              \\
               Matriculation number: & 3367576                 \\
               Supervisor:           & Prof. Dr. Michael Gertz \\
               Date of submission:   & \today
          \end{tabular}
     }

@@

\subsection{Example(s) of CSS Problems Today}
\begin{enumerate}
     \item CSS incomplete in governmental administration
           \begin{enumerate}
                \item identity card renewal
                \item change of home address
                \item change of residency status
           \end{enumerate}

@@

\subsection{Solution for CSS Problems}
\begin{enumerate}
     \item One CSS providing company, which integrates multiple / all EA
     \item One identity, profile, address, phone number, location, ...
     \item Easy management of identity used by multiple enterprises / organizations
\end{enumerate}

\subsection{Integration necessity}
\begin{enumerate}
     \item Each enterprise / organization has its own identities, profiles, etc. in multiple systems
     \item The CSS providing company needs to manage those systems / data of each enterprise / organization
     \item Enterprise Integration solves this Problem
\end{enumerate}

@@

\subsection{Integration Challenges}
\begin{enumerate}
     \item Heterogeneous Enterprise Architecture Systems
           \begin{enumerate}
                \item Different Applications
                \item Different Application Vendors
                \item Different / No Application Interfaces
                \item Legacy Systems
           \end{enumerate}

@@

\subsection{Presented Solutions}
\begin{enumerate}
     \item Messaging Integration
           \begin{enumerate}
                \item Loose Coupling
                      \begin{enumerate}
                           \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
                           \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
                           \item Loose Coupling allows Reuse of "Modules" => faster development
                      \end{enumerate}

@@

\chapter{Foundation and related work}

\section{Customer Self-Service}

\subsection{Definition}
\begin{enumerate}
     \item Definition in the context of the thesis
\end{enumerate}

\subsection{Documentation}
\begin{enumerate}
     \item How can CSS-Scenarios be documented?
\end{enumerate}

\subsection{List of Scenarios}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Finding relevant EAPs
     \item Requirement analysis of business Connector
     \item Interface definition of business connector
\end{enumerate}

\section{Architecture Patterns}
\subsection{Definition}
\begin{enumerate}
     \item Definition
     \item Metadata
     \item Views
     \item Architecture bricks
     \item Data bricks
     \item Business processes
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Basis for real-life enterprise architectures
     \item Provides architecture and data bricks the integration can build up on
\end{enumerate}

\subsection{Architecture- and Data bricks}
\begin{enumerate}
     \item Description of EAPs used in the thesis
     \item Reasons why each EAP is relevant for CSS
           \begin{enumerate}
                \item Derived by comparing CSS-Scenarios with business processes
           \end{enumerate}
     \item Architecture bricks and data bricks of EAPs relevant for CSS-Scenarios
     \item Documentation of resulting Architecture and data bricks
\end{enumerate}

\subsection{Requirements of Enterprise Architecture}
\begin{enumerate}
     \item List of requirements towards the integration Architecture
           \begin{enumerate}
                \item Adapters for systems
                \item Required Format of incoming data
           \end{enumerate}
\end{enumerate}

\section{Business Connector}

\subsection{Definition}
\begin{enumerate}
     \item Provides functionality of "external" service provider
     \item Purpose is to simplify integration
     \item Can be assumed to provide sufficient interfaces
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Provides interface for CSS functionalities
     \item Should be integrated in architecture and data bricks
\end{enumerate}

\subsection{Documentation}
\begin{enumerate}
     \item How to document the business Connector in this context

     \item List of provided functionalities along with their interfaces
           \begin{enumerate}
                \item Derived from CSS-Scenarios
                \item Derived from IDAS Connector
           \end{enumerate}

@@

\section{Integration Patterns}

\subsection{Definition}
\begin{enumerate}
     \item Messaging Methodology
     \item Patterns describe often solved messaging problems
\end{enumerate}

\subsection{Purpose in Thesis}
\begin{enumerate}
     \item Already explained in Motivation?
\end{enumerate}

\subsection{Patterns used in Thesis}
\begin{enumerate}
     \item Description of Patterns later used in the integration architecture
\end{enumerate}

@@

\chapter{My contribution}

\section{Overview}

\section{Requirements}

\subsection{Requirements of Enterprise Architecture}

\subsection{Requirements of Business Connector}

\subsection{Requirements of Integration System}

\section{Scenario Integrations}
\begin{enumerate}
     \item Look at integration architecture for each CSS-Scenario
\end{enumerate}

\subsection{Integration Architecture Documentation Method}
\begin{enumerate}
     \item Entity Diagram(s)
     \item Flow Diagram(s)
     \item etc.
\end{enumerate}

\subsection{Scenario1}
\begin{enumerate}
     \item Description of Scenario
\end{enumerate}

\subsubsection{Scenario1 Integration Architecture}
\begin{enumerate}
     \item Entity Diagram(s)
     \item Flow Diagram(s)
     \item etc.
\end{enumerate}

\subsubsection{System Integration}
\begin{enumerate}
     \item Explanation how the systems are integrated
     \item Why was each pattern used?
     \item How are requirements met?
\end{enumerate}

\subsubsection{Data Integration}
\begin{enumerate}
     \item Explanation how the data objects are integrated
     \item Why was data transformed / mapped?
     \item How are requirements met
\end{enumerate}

\subsection{Scenario2}

\subsubsection{Scenario2 Integration Architecture}

\subsubsection{System Integration}

\subsubsection{Data Integration}

\section{Operating Manual}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Experimental evaluation}

\section{Customer Landscape}

\section{Customer Requirements}

\section{Integration}

\subsection{Using the Operating Manual}

\subsection{Relevant Bricks}

\subsubsection{Data Bricks}

\subsubsection{Architecture Bricks}

\subsection{Resulting Integration}

\subsubsection{Integration Documentation}

\subsubsection{System Integration}

\subsubsection{Data Integration}

\section{Evaluation}

\subsection{Satisfaction of Requirements}

\subsubsection{Enterprise Architecture Requirements}

\subsubsection{Customer Requirements}

\subsubsection{Business Connector Requirements}

\subsubsection{Integration Architecture Requirements}

\subsection{Resource-Heaviness}

\subsubsection{Required time for application}

\subsubsection{Size of Resulting System}

\subsubsection{Increasing cost due to scaling}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Summary and outlook}
